A Classical Density-Functional Theory for Describing Water Interfaces

### 2012-06-26 papers/water-SAFT/paper.tex
add fixme to water paper Tested everything on node08.

A number of exact properties are easily achieved in the
density-functional framework, such as the contact-value theorem, which
ensures a correct free energy of hydration for small hard solutes.
Much of the research on classical density-functional theory has
focused on the hard-sphere fluid~\cite{curtin1985, rosenfeld1989,
  rosenfeld1993, rosenfeld1997, tarazona1997, tarazona2000}, which has
led to a number of sophisticated functionals, such as the
fundamental-measure theory (FMT) functionals\cite{rosenfeld1989,
  rosenfeld1993, rosenfeld1997, tarazona1997, tarazona2000,
  roth2002whitebear}, which are entirely expressed as an integral of
local functions of a few convolutions of the density that can be
efficiently computed.  We will use the White Bear version of the FMT
functional\cite{roth2002whitebear}.  In the homogeneous limit, this
functional reduces to the Carnahan-Starling equation of state, and in
the strongly-confined limit of a highly confined cavity, it reproduces
the exact free energy.

>>>>

A number of exact properties are easily achieved in the
density-functional framework, such as the contact-value theorem, which
ensures a correct free energy of hydration \fixme{change this to
  excess chemical potential?} for small hard solutes.
Much of the research on classical density-functional theory has
focused on the hard-sphere fluid~\cite{curtin1985, rosenfeld1989,
  rosenfeld1993, rosenfeld1997, tarazona1997, tarazona2000}, which has
led to a number of sophisticated functionals, such as the
fundamental-measure theory (FMT) functionals\cite{rosenfeld1989,
  rosenfeld1993, rosenfeld1997, tarazona1997, tarazona2000,
  roth2002whitebear}, which are entirely expressed as an integral of
local functions of a few convolutions of the density that can be
efficiently computed.  We will use the White Bear version of the FMT
functional\cite{roth2002whitebear}.  In the homogeneous limit, this
functional reduces to the Carnahan-Starling equation of state, and in
the strongly-confined limit of a highly confined cavity, it reproduces
the exact free energy.
